\huge Tor's Usability for Censorship Circumvention

### 2016-04-07 pets2017-paper/pets2017-paper.tex
Mention instrumentation and video recording.

>>>>

We prepared special instrumented versions of both versions of Tor Launcher.
The instrumentation logs recorded every meaningful interaction with the interface---every
button press, every menu selection, every screen change---along with a timestamp.
The logs enabled us to calculate statistics such as the success rate
for each condition.

We recorded a video of the contents of the computer screen throughout each session.
Review of the videos revealed details not captured by the instrumentation logs alone,
such as participants' web searching and inspection of system networking settings.
